Optimal (Multiway) Spatial Joins

### 2024-05-24 msj.tex
yufei

\extraspacing {\bf Generating $\bm{\J^*}$.} Take an arbitrary $(k-2)$-tuple $\bm{t} = (r'_1, r'_2, ...,$ $r'_{k-2}) \in \J(R_1', R'_2, ..., R'_{k-2})$. The reader should recall from Section~\ref{sec:bricks} that
\myitems{
    \item $B_\bm{t}$ is $\bigcap_{i=1}^{k-2} \bm{t}[i]$, i.e., the intersection of $r'_1, r'_2, ..., r'_{k-2}$;
    \item $\gleft(\bm{t})$ is the $r'_i$ ($1 \le i \le k-2$) with $\xleft(r'_i) = \xleft(B_\bm{t})$;
    \item $\gbot(\bm{t})$ is the $r'_i$ ($1 \le i \le k-2$) with $\ybot(r'_i) = \ybot(B_\bm{t})$.
}
We now introduce:
% \myitems{
%     \item $\cross(r_a, B; H)$, the set of segments in $H$ that cross $r_a$ and $B$;
%     \item $\cross(r_b, B; V)$, the set of segments in $V$ that cross $r_b$ and $B$.
% }
\myeqn{
    \dcross_H(\bm{t}) = \set{h \in H \mid \text{$h$ crosses both $B_\bm{t}$ and $\gleft(\bm{t})$}} \label{eqn:dcross-H} \\
    \dcross_V(\bm{t}) = \set{h \in H \mid \text{$v$ crosses both $B_\bm{t}$ and $\gbot(\bm{t})$}}. \nn
    %\label{eqn:dcross-H} 
}
The prefix ``d-'' stands for double. These sets have important properties as stated in the next lemma, whose proof can be found in Appendix~\ref{app:hv}:

@@

Lemma~\ref{lmm:hv:type1:properties} assures us that the set $\J^*$ thus computed indeed satisfies \eqref{eqn:hv:type1:J*}. Furthermore, if we are given $\dcross_H(\bm{t})$ and $\dcross_V(\bm{t})$ for each $\bm{t}$, Lemma~\ref{lmm:hv:type1:properties} further asserts that the above algorithm runs in $O(1 + k \cdot |\J^*|) = O(1 + k \cdot \out)$ time.

>>>>

\extraspacing {\bf Generating $\bm{\J^*}$.} Take any $(k-2)$-tuple $\bm{t} = (r'_1, r'_2, ...,$ $r'_{k-2}) \in \J(R_1', R'_2, ..., R'_{k-2})$. The reader should recall from Section~\ref{sec:bricks} that
\myitems{
    \item $B_\bm{t}$ is $\bigcap_{i=1}^{k-2} \bm{t}[i] = \bigcap_{i=1}^{k-2} r'_i$;
    \item $\gleft(\bm{t})$ is the $r'_i$ ($1 \le i \le k-2$) with $\xleft(r'_i) = \xleft(B_\bm{t})$;
    \item $\gbot(\bm{t})$ is the $r'_i$ ($1 \le i \le k-2$) with $\ybot(r'_i) = \ybot(B_\bm{t})$.
}
We now introduce:
% \myitems{
%     \item $\cross(r_a, B; H)$, the set of segments in $H$ that cross $r_a$ and $B$;
%     \item $\cross(r_b, B; V)$, the set of segments in $V$ that cross $r_b$ and $B$.
% }
\myeqn{
    \dcross_H(\bm{t}) = \set{h \in H \mid \text{$h$ crosses both $B_\bm{t}$ and $\gleft(\bm{t})$}} \label{eqn:dcross-H} \\
    \dcross_V(\bm{t}) = \set{h \in H \mid \text{$v$ crosses both $B_\bm{t}$ and $\gbot(\bm{t})$}}. \nn
    %\label{eqn:dcross-H} 
}
The prefix ``d-'' stands for ``double''. These sets have important properties as stated in the next lemma, whose proof can be found in Appendix~\ref{app:hv}:

@@

By statements (b) and (c) of Lemma~\ref{lmm:hv:type1:properties}, the set $\J^*$ thus computed indeed satisfies \eqref{eqn:hv:type1:J*}. Furthermore, if we are given $\dcross_H(\bm{t})$ and $\dcross_V(\bm{t})$ for each $\bm{t}$, statement (a) of Lemma~\ref{lmm:hv:type1:properties} assures us that the above algorithm runs in $O(1 + k \cdot |\J^*|) = O(1 + k \cdot \out)$ time.
